Supplemental material

### 2024-04-29 paper/resp_referee.qmd
update article
V2.1

*The modelled of the input time series is now describe more precisely in section 2 (previous section 1). $TC_t$ is here considered as deterministic*

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methodes (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher;*

@@

*In local polynomial smoothing, the notion of bias is associated to the approximation error of the smoothed series by a polynomial degree of order $d$.*
*If the moving average $\theta$ preserve a polynomial of degree $d$, the bias at the date $t$ is then:*
$$
\mathbb E[\hat \mu(t)] - \mu(t)=\sum_{j=d+1}^{+\infty}\frac{\mu^{(j)}(t)}{j!}\sum_{k=-h}^k\theta_k k^j
$$
*It is then not directly related to the phase shift.*

@@

*More details are added to this section. The definition is more general than the polynomial ind*

@@

>>>>

*The modelled of the input time series is now describe more precisely in section 2 (previous section 1).* 
*$TC_t$ is here considered as deterministic*

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methodes (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher.*

@@

*In local polynomial smoothing, the notion of bias is associated to the approximation error of the smoothed series by a polynomial degree of order $d$.*
*If the moving average $\theta$ preserve a polynomial of degree $d$, the bias at the date $t$ is then:*
$$
\mathbb E[\hat \mu(t)] - \mu(t)=\sum_{j=d+1}^{+\infty}\frac{\mu^{(j)}(t)}{j!}\sum_{k=-h}^h\theta_k k^j
$$
*It is then not directly related to the phase shift.*

@@

*More details were added to this section to clarify the definition: the forecasts are obtained so that the filtered extended series (input + forecast) with the symmetric filter is equal to the filtered extended series with the asymmetric filters.* 
*It doesn't correspond to the forecasts of the polynomial model.*
*The definition is not restricted to moving averages build with local polynomial, the forecasts do not assumed polynomial trend model.*

@@

*A reading note is added to figure 5 to improve its reading*

### 2024-04-29 paper/supp_material.qmd
V2.1

@@

::: {#fig-nn-localparam}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_lp_localparam.pdf")
```
Note: nearest bandwidth moving average are used to estimate slope and concavity.
We thus do not distinguish local parametrisation and final local parametrisation which asumptions might not be plausible.
Indeed, using the same framework as for fixed bandwidth, the final local parametrisation for real time estimates would implie modelling a polynomial of degree 2 or 3 other 25 months (which doesn't seem plausible).

@@

>>>>

```{r}
#| include: false
library(kableExtra)

```

@@

::: {#fig-nn-localparam}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_lp_localparam.pdf")
```

\justifying
*Note: nearest bandwidth moving average are used to estimate slope and concavity.*
*We thus do not distinguish local parametrisation and final local parametrisation which asumptions might not be plausible.*
*Indeed, using the same framework as for fixed bandwidth, the final local parametrisation for real time estimates would implie modelling a polynomial of degree 2 or 3 other 25 months (which doesn't seem plausible).*

@@

::: {#tbl-simulrev-q}
```{r}
#| echo: false
rev_table <- readRDS("data/simulations_revisions_q.RDS")
pack_row_index = c("$MAE_{fe}(q) = \\mathbb E\\\\left[\\\\left|(TC_{t|t+q} -  TC_{t|last})/TC_{t|last}\\\\right|\\\\right]$" = nrow(rev_table) / 2,
                   "$MAE_{ce}(q)=\\mathbb E\\\\left[
\\\\left|(TC_{t|t+q} - TC_{t|t+q+1})/TC_{t|t+q+1}\\\\right|
\\\\right]$" = nrow(rev_table) / 2)
rev_table  %>%
  kable(format.args = list(digits = 2,
                           decimal.mark = "."),
        align = "c", booktabs = T, row.names = FALSE, 
        escape = FALSE,format = "latex") %>%  
  # kable_styling(latex_options=c(#"striped",  
  #   "hold_position")) %>% 
  pack_rows(index = pack_row_index, escape = FALSE) # %>%
    # add_footnote_kable(stop_centering = TRUE)
```

Average of the relative deviations of the revisions for the different filters on simulated quarterly series with medium variability.
:::
